---
title: "Plots and graphs for thesis"
output: html_notebook
---
```{r echo = FALSE}
library(tidyverse)
library(writexl)
library(plyr)
library(lubridate)
library(plotly)
library(dplyr)
library(corrplot)
```


## Exchange rate and sentiment: is there a connection?
Before we can start with our machine learning model we need to understand the relationship between the two variables, therefore we should calculate covariance. This measures the direction of a relationship between the two variables.

# First step: creating a dataframe from the csv
```{r}
btc_exchange_rate_history <- read.csv("D:/Suli/Szakdolgozat1/development_n_stuff/aggregated_data.csv") %>%
                             select(-X) %>%
                             mutate(created_at = as_date(created_at))



btc_usd_tweets_combined <- read.csv("D:/Suli/Szakdolgozat1/data_to_be_cleaned/coin_Bitcoin.csv") %>%
                           mutate(Date = as_date(Date)) %>%
                           mutate(year = year(Date), month = month(Date), day = day(Date)) %>%
                           mutate(Date = make_date(year,month,day)) %>% 
                           mutate(xchange_rate_change = Close - Open) %>%
                           filter(Date >= "2019-01-01" & Date <= "2022-03-30") %>%
                           inner_join(btc_exchange_rate_history, by = c("Date" = "created_at")) %>% 
                           select(c(-year,-month,-day))

```

```{r}
btc_sent_lineplot <- plot_ly(data = btc_usd_tweets_combined, x = ~Date, y = ~xchange_rate_change, name ="BTC 
                             change", type = 'scatter', mode = 'lines', color = 'red') %>%
                     add_trace(data = btc_usd_tweets_combined, x = ~Date, y = ~daily_avg_sent, yaxis = "y2", name = 'Avg. sentiment', 
                               mode ='lines', color = 'blue') %>%
                     layout(title = "Bitcoin exchange rate change compared to previous day's closing rate",
                            legend = list(x = 1.2),
                            paper_bgcolor='rgb(255, 255, 255)', plot_bgcolor='rgb(255, 255, 255)',
                            xaxis = list(title = 'Date', range = list("2019-01-01 00:00:00", "2019-12-31 23:59:59"), rangeslider =
                                         list(type = "date", visible = T),
                                         list(dtickrange=list(NULL, 1000), value="%H:%M:%S.%L ms"),
                                         list(dtickrange=list(1000, 60000), value="%H:%M:%S s"),
                                         list(dtickrange=list(60000, 3600000), value="%H:%M m"),
                                         list(dtickrange=list(3600000, 86400000), value="%H:%M h"),
                                         list(dtickrange=list(86400000, 604800000), value="%e. %b d"),
                                         list(dtickrange=list(604800000, "M1"), value="%e. %b w"),
                                         list(dtickrange=list("M1", "M12"), value="%b '%y M"),
                                         list(dtickrange=list("M12", NULL), value="%Y Y"),
                                         rangeselector=list(
                                           buttons=list(
                                           list(count=1, label="1M", step="month", stepmode="backward"),
                                           list(count=6, label="6M", step="month", stepmode="backward"),
                                           list(count=1, label="1Y", step="year", stepmode="backward"),
                                           list(count=1, label="YTD", step="year", stepmode="todate"),
                                           list(step="all", label = "ALL")
                                           )),
                                         list(dtick = "M1", tickformat="%b\n%Y",
                                              ticklabelmode="period")),
                            yaxis = list(title = "BTC exchange rate change",
                                         range = c(min(btc_usd_tweets_combined$xchange_rate_change), 
                                                   max(btc_usd_tweets_combined$xchange_rate_change)),
                                         gridcolor = 'rgb(255,255,255)',
                                         showgrid = TRUE,
                                         showline = FALSE,
                                         showticklabels = TRUE,
                                         tickcolor = 'rgb(140, 140, 140)',
                                         ticks = 'outside',
                                         zeroline = FALSE),
                            yaxis2 = list(title = "Daily average sentiment", overlaying = "y", side = "right", range = 
                                            c(min(btc_usd_tweets_combined$daily_avg_sent), 
                                              max(btc_usd_tweets_combined$daily_avg_sent)))
                            )
                     

btc_sent_lineplot
```

# Second step: plotting the data on a scatterplot
todo: exchange price changehez nézni, nem az árhoz


```{r}
btc_sent_scatterplot <- plot_ly(data = btc_usd_tweets_combined, y =  ~daily_avg_sent, x = ~xchange_rate_change,
                            marker = list(size = 4,
                             color = 'rgba(255, 182, 193, .9)',
                             line = list(color = 'rgba(152, 0, 0, .8)', width = 1))) %>%
                        layout(yaxis = list(title = "Daily average sentiment"),
                               xaxis = list(title = "BTC exchange rate change"))

btc_sent_scatterplot
```

# Third step: calculate covariance and correlation

```{r}
btc_cov <- cov(btc_usd_tweets_combined$daily_avg_sent,btc_usd_tweets_combined$xchange_rate_change, method = "pearson")

btc_cov

```
A positive covariance means that the two variables tend to increase or decrease together. 
Correlation helps us analyze the effect of changes made in one variable over the other variable of the dataset.
Now that we know this, we should calculate the strength of the relationship between two, numerically measured, continuous variables.

```{r}
btc_cor <- cor(btc_usd_tweets_combined$daily_avg_sent,btc_usd_tweets_combined$xchange_rate_change, method = "pearson")

btc_cor
```


