---
title: "Plots and graphs for thesis"
output: 
  html_document
---
# Exchange rate and sentiment: is there a connection?
Before we can start with our machine learning model we need to understand the relationship between the two variables, therefore we should calculate covariance. This measures the direction of a relationship between the two variables.

***
### Loading libraries to be used
```{r, warning=FALSE,message=FALSE}
library(tidyverse)
library(writexl)
library(plyr)
library(lubridate)
library(plotly)
library(dplyr)
library(corrplot)
library(formatR)
```

***
## First step: creating a dataframe from the csv
```{r, tidy=TRUE}
btc_exchange_rate_history <- read.csv("D:/Suli/Szakdolgozat1/development_n_stuff/aggregated_data.csv") %>%
                             select(-X) %>%
                             mutate(created_at = as_date(created_at))



btc_usd_tweets_combined <- read.csv("D:/Suli/Szakdolgozat1/data_to_be_cleaned/coin_Bitcoin.csv") %>%
                           mutate(Date = as_date(Date)) %>%
                           mutate(year = year(Date), month = month(Date), day = day(Date)) %>%
                           mutate(Date = make_date(year,month,day)) %>% 
                           mutate(xchange_rate_change = Close - Open) %>%
                           filter(Date >= "2019-01-01" & Date <= "2022-03-30") %>%
                           inner_join(btc_exchange_rate_history, by = c("Date" = "created_at")) %>% 
                           select(c(-year,-month,-day))

```

***
## Second step: plotting exchange rate change and average sentiment for further insights
```{r, tidy=TRUE, warning=FALSE, fig.width=10, fig.height=8, fig.align='center'}
btc_sent_lineplot <- plot_ly(data = btc_usd_tweets_combined, x = ~Date, y = ~xchange_rate_change, name ="BTC change", type = 'scatter', 
                             mode = 'lines', color = 'red') %>%
                     add_trace(data = btc_usd_tweets_combined, x = ~Date, y = ~daily_avg_sent, yaxis = "y2", name = 'Avg. sentiment', 
                               mode ='lines', color = 'blue') %>%
                     layout(title = "Bitcoin exchange rate change compared to previous day's closing rate",
                            margin = list(t = 150),
                            legend = list(x = 1.1),
                            paper_bgcolor='rgb(255, 255, 255)', plot_bgcolor='rgb(255, 255, 255)',
                            xaxis = list(title = 'Date', range = list("2019-01-01 00:00:00", "2019-12-31 23:59:59"), rangeslider =
                                         list(type = "date", visible = T),
                                         list(dtickrange=list(NULL, 1000), value="%H:%M:%S.%L ms"),
                                         list(dtickrange=list(1000, 60000), value="%H:%M:%S s"),
                                         list(dtickrange=list(60000, 3600000), value="%H:%M m"),
                                         list(dtickrange=list(3600000, 86400000), value="%H:%M h"),
                                         list(dtickrange=list(86400000, 604800000), value="%e. %b d"),
                                         list(dtickrange=list(604800000, "M1"), value="%e. %b w"),
                                         list(dtickrange=list("M1", "M12"), value="%b '%y M"),
                                         list(dtickrange=list("M12", NULL), value="%Y Y"),
                                         rangeselector=list(
                                           buttons=list(
                                           list(count=1, label="1M", step="month", stepmode="backward"),
                                           list(count=6, label="6M", step="month", stepmode="backward"),
                                           list(count=1, label="1Y", step="year", stepmode="backward"),
                                           list(count=1, label="YTD", step="year", stepmode="todate"),
                                           list(step="all", label = "ALL")
                                           )),
                                         list(dtick = "M1", tickformat="%b\n%Y", ticklabelmode="period")),
                            yaxis = list(title = "BTC exchange rate change",
                                         range = c(min(btc_usd_tweets_combined$xchange_rate_change), 
                                                   max(btc_usd_tweets_combined$xchange_rate_change)),
                                         gridcolor = 'rgb(255,255,255)',
                                         showgrid = TRUE,
                                         showline = FALSE,
                                         showticklabels = TRUE,
                                         tickcolor = 'rgb(140, 140, 140)',
                                         ticks = 'outside',
                                         zeroline = FALSE),
                            yaxis2 = list(title = "Daily average sentiment", overlaying = "y", side = "right", range = 
                                            c(min(btc_usd_tweets_combined$daily_avg_sent), 
                                              max(btc_usd_tweets_combined$daily_avg_sent)))
                            )
                     

btc_sent_lineplot
```
***
## Third step: plotting the data on a scatterplot
todo: exchange price changehez nézni, nem az árhoz


```{r, tidy=TRUE, warning=FALSE, message=FALSE, fig.align='center'}
btc_sent_scatterplot <- plot_ly(data = btc_usd_tweets_combined, y =  ~daily_avg_sent, x = ~xchange_rate_change,
                            marker = list(size = 4,
                             color = 'rgba(255, 182, 193, .9)',
                             line = list(color = 'rgba(152, 0, 0, .8)', width = 1))) %>%
                        layout(yaxis = list(title = "Daily average sentiment"),
                               xaxis = list(title = "BTC exchange rate change"))

btc_sent_scatterplot
```

***
## Fourth step: calculate covariance and correlation

```{r, tidy=TRUE}
btc_cov <- cov(btc_usd_tweets_combined$daily_avg_sent,btc_usd_tweets_combined$xchange_rate_change, method = "pearson")

btc_cov

```
A positive covariance means that the two variables tend to increase or decrease together. 
Correlation helps us analyze the effect of changes made in one variable over the other variable of the dataset.
Now that we know this, we should calculate the strength of the relationship between two, numerically measured, continuous variables.

```{r, tidy=TRUE}
btc_cor <- cor(btc_usd_tweets_combined$daily_avg_sent,btc_usd_tweets_combined$xchange_rate_change, method = "pearson")

btc_cor
```
> One of the most common ways to quantify a relationship between two variables is to use the Pearson correlation coefficient, which is a measure of the linear association between two variables.
>
> It always takes on a value between -1 and 1 where:
>
> * -1 indicates a perfectly negative linear correlation between two variables
> * 0 indicates no linear correlation between two variables
> * 1 indicates a perfectly positive linear correlation between two variables
>
>Often denoted as r, this number helps us understand the strength of the relationship between two variables. The closer r is to zero, the weaker the relationship between the two variables.

A weak correlation indicates that there is minimal relationship between the variables.

After reading some scientific papers I concluded that continuing down this path would bear no plausible outcome, so I decided to look at some other trend measures that seem promising.