---
title: "Forecast Bitcoin exchange rate using Prophet"
output: 
  html_document:
#    number_sections: true
---
```{r, warning=FALSE,message=FALSE}
library(prophet)
library(tidyverse)
library(caret)
library(caTools)
library(anytime)
library(gdata)
library(ehaGoF)
library(readr)
```

Load cleaned data:

```{r, tidy = TRUE}
final_df <- readxl::read_xlsx("D:/Suli/Szakdolgozat1/clean data/data_for_training.xlsx")
```

Feature selection:

```{r}
set.seed(123)
#control <- rfeControl(functions=rfFuncs, method="cv", number=10)
#results <- rfe(final_df[,4:10], final_df[,3], sizes=c(4:10), rfeControl=control)
```

Function to loop through regressor values and predict their future values for use:

```{r, tidy = TRUE}
predict_regressors <- function(columns, source_dataframe){
  future_regressors_df <- data.frame(Date = seq(as.Date("2019/1/1"), as.Date("2022/05/29"), by = "days"))
  f_model <- 0
  for (col in columns){
    temp_df <- cbind(source_dataframe$Date,source_dataframe[,col])
    names(temp_df)[names(temp_df) == "source_dataframe$Date"] <- "ds"
    names(temp_df)[names(temp_df) == col] <- "y"
    f_model <- prophet(temp_df, weekly.seasonality = FALSE, changepoint.range = 1, changepoint.prior.scale = 0.6)
    f_future <- make_future_dataframe(f_model, periods = 60)
    temp_df <- predict(f_model,f_future)
    future_regressors_df <- cbind(future_regressors_df,temp_df$yhat)
    names(future_regressors_df)[names(future_regressors_df) == "temp_df$yhat"] <- col
  }
  return(future_regressors_df)
}
```


```{r}
test_df <- predict_regressors(c('Nr_of_Reddit_posts','Google_Trends_indicator','Price_change','Nr_of_tweets','Nr_of_Bitcoin_transactions','Nr_of_unique_Bitcoin_addresses','Bitcoin_transaction_volume','Wikipedia_searches_Bitcoin'), final_df)
```

Rename date to ds and column to be predicted to y:

```{r, tidy = TRUE}
ml_df <- final_df %>%
         select("Closing_price") %>%
         rename("y" = "Closing_price") %>%
         cbindX(test_df) %>%
         rename("ds" = "Date")
```

Split to train and test dataset:

```{r, tidy = TRUE}
sample <- sample.split(ml_df$ds, SplitRatio= 0.7)
train <- subset(ml_df, sample == TRUE)
test <- subset(ml_df, sample == FALSE)
```

Add all variables:

```{r, tidy = TRUE}
model <- prophet(daily.seasonality = TRUE)
model <- add_regressor(model,'Nr_of_Reddit_posts', standardize = FALSE)
model <- add_regressor(model,'Google_Trends_indicator', standardize = FALSE)
model <- add_regressor(model,'Price_change', standardize = FALSE)
model <- add_regressor(model,'Nr_of_tweets', standardize = FALSE)
model <- add_regressor(model,'Nr_of_Bitcoin_transactions', standardize = FALSE)
model <- add_regressor(model,'Nr_of_unique_Bitcoin_addresses', standardize = FALSE)
model <- add_regressor(model,'Bitcoin_transaction_volume', standardize = FALSE)
model <- add_regressor(model,'Wikipedia_searches_Bitcoin', standardize = FALSE)

```

```{r, tidy = TRUE}
model <- fit.prophet(model, ml_df)
```

```{r, tidy = TRUE}
forecast <- predict(model,ml_df)

tail(forecast[c('ds','yhat', 'yhat_lower','yhat_upper')])
```

```{r, tidy = TRUE}
plot(model, forecast)
```

Cross-validation:

```{r, tidy = TRUE}
df_cv <- cross_validation(model, initial = 821, horizon = 60, period = 30, units = "days")

head(df_cv)
```
```{r, tidy = TRUE}
df_p <- performance_metrics(df_cv)

head(df_p)
```

```{r,tidy = TRUE}
write_rds(forecast,"forecast.Rds")
write_rds(model, "model.Rds")
write_rds(ml_df, "training_df.Rds")
```

Relative RMSE of 60 days of prediction:

There are two ways to get relative RMSE (or normalized RMSE):

- Divide RMSE by standard deviation of observed values.
- Divide RMSE by difference between max and min of observed values.

```{r, tidy = TRUE}
rel_RMSE <- sqrt( mean( (forecast$yhat-final_df$Closing_price)^2) ) / (max(final_df$Closing_price) - min(final_df$Closing_price) )
print(rel_RMSE)

rel_RMSE_2 <- ehaGoF::gofRRMSE(final_df$Closing_price,forecast$yhat)
print(rel_RMSE_2)
```

