---
title: "Plots and graphs for thesis"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache = TRUE)
```

# Exchange rate and social media: is there a connection?
Before we can start with our machine learning model we need to understand the relationship between the two variables, therefore we should calculate covariance. This measures the direction of a relationship between the two variables.

***
### Loading libraries to be used
```{r, warning=FALSE,message=FALSE}

library(tidyverse)
library(padr)
library(tidytext)
library(tm)
library(writexl)
library(plyr)
library(lubridate)
library(anytime)
library(plotly)
library(dplyr)
library(corrplot)
library(formatR)
library(htmltools)
library(ggpubr)
library(textstem)
library(vader)
library(zoo)
library(ggplot2)

```

***
## First step: creating a dataframe from the csv
```{r, tidy=TRUE}

btc_exchange_rate_history <- read.csv("D:/Suli/Szakdolgozat1/clean data/aggregated_data.csv") %>%
                             select(-X) %>%
                             mutate(created_at = as_date(created_at))



btc_usd_tweets_combined <- read.csv("D:/Suli/Szakdolgozat1/clean data/Bitcoin_exchage_rates.csv") %>%
                           mutate(Date = as_date(Date)) %>%
                           mutate(xchange_rate_change = Close - Open) %>%
                           filter(Date >= "2019-01-01" & Date <= "2022-03-30") %>%
                           inner_join(btc_exchange_rate_history, by = c("Date" = "created_at"))


```

***
## Second step: plotting exchange rate change and average sentiment for further insights, taking a look at distribution
```{r, tidy=TRUE, warning=FALSE, fig.width=10, fig.height=8, fig.align='center'}

btc_sent_lineplot <- plot_ly(data = btc_usd_tweets_combined, x = ~Date, y = ~xchange_rate_change, name ="BTC change", type =
                               'scatter', 
                             mode = 'lines', color = 'red') %>%
                     add_trace(data = btc_usd_tweets_combined, x = ~Date, y = ~daily_avg_sent, yaxis = "y2", 
                               name = 'Avg. sentiment', mode ='lines', color = 'blue') %>%
                     layout(title = "Bitcoin exchange rate change compared to previous day's closing rate",
                            margin = list(t = 150),
                            legend = list(x = 1.1),
                            paper_bgcolor='rgb(255, 255, 255)', plot_bgcolor='rgb(255, 255, 255)',
                            xaxis = list(title = 'Date', range = list("2019-01-01 00:00:00", "2019-12-31 23:59:59"), 
                                         rangeslider =
                                         list(type = "date", visible = T),
                                         list(dtickrange=list(NULL, 1000), value="%H:%M:%S.%L ms"),
                                         list(dtickrange=list(1000, 60000), value="%H:%M:%S s"),
                                         list(dtickrange=list(60000, 3600000), value="%H:%M m"),
                                         list(dtickrange=list(3600000, 86400000), value="%H:%M h"),
                                         list(dtickrange=list(86400000, 604800000), value="%e. %b d"),
                                         list(dtickrange=list(604800000, "M1"), value="%e. %b w"),
                                         list(dtickrange=list("M1", "M12"), value="%b '%y M"),
                                         list(dtickrange=list("M12", NULL), value="%Y Y"),
                                         rangeselector=list(
                                           buttons=list(
                                           list(count=1, label="1M", step="month", stepmode="backward"),
                                           list(count=6, label="6M", step="month", stepmode="backward"),
                                           list(count=1, label="1Y", step="year", stepmode="backward"),
                                           list(count=1, label="YTD", step="year", stepmode="todate"),
                                           list(step="all", label = "ALL")
                                           )),
                                         list(dtick = "M1", tickformat="%b\n%Y", ticklabelmode="period")),
                            yaxis = list(title = "BTC exchange rate change",
                                         range = c(min(btc_usd_tweets_combined$xchange_rate_change), 
                                                   max(btc_usd_tweets_combined$xchange_rate_change)),
                                         gridcolor = 'rgb(255,255,255)',
                                         showgrid = TRUE,
                                         showline = FALSE,
                                         showticklabels = TRUE,
                                         tickcolor = 'rgb(140, 140, 140)',
                                         ticks = 'outside',
                                         zeroline = FALSE),
                            yaxis2 = list(title = "Daily average sentiment", overlaying = "y", side = "right", range = 
                                            c(min(btc_usd_tweets_combined$daily_avg_sent), 
                                              max(btc_usd_tweets_combined$daily_avg_sent)))
                            )
                     

btc_sent_lineplot

```

```{r, tidy=TRUE, warning=FALSE, message=FALSE, fig.align='center'}
btc_exchange_rate_history$daily_avg_sent <- scale(btc_exchange_rate_history$daily_avg_sent)
```


```{r, tidy=TRUE, warning=FALSE, message=FALSE, fig.align='center'}
plot(density(btc_exchange_rate_history$daily_avg_sent), type="n", main = "Distribution of average daily sentiment")
polygon(density(btc_exchange_rate_history$daily_avg_sent), col="red", border="gray")

```

```{r, tidy = TRUE}

shapiro.test(btc_exchange_rate_history$daily_avg_sent)

```

```{r, tidy=TRUE, warning=FALSE, message=FALSE, fig.align='center'}

plot(density(btc_usd_tweets_combined$xchange_rate_change), type="n", main = "Distribution of Bitcoin exchange rate change")
polygon(density(btc_usd_tweets_combined$xchange_rate_change), col="red", border="gray")

```

```{r}

shapiro.test(btc_usd_tweets_combined$xchange_rate_change)

```

These seem like pretty standard normal distributions, so we can use Pearson Correlation Coefficient calculation later on.

***
## Third step: plotting the data on a scatterplot

```{r, tidy=TRUE, warning=FALSE, message=FALSE, fig.align='center'}

btc_sent_scatterplot <- plot_ly(data = btc_usd_tweets_combined, y =  ~daily_avg_sent, x = ~xchange_rate_change,
                            marker = list(size = 4,
                             color = 'rgba(255, 182, 193, .9)',
                             line = list(color = 'rgba(152, 0, 0, .8)', width = 1))) %>%
                        layout(yaxis = list(title = "Daily average sentiment"),
                               xaxis = list(title = "BTC exchange rate change (USD)")) %>%
                        htmltools::div(align="center" )

btc_sent_scatterplot

```
The plot shows that there is no distinguishable relationship between these variables, but I still wanted to do the covariance and correlation calculation to get the mathematical results.

***
## Fourth step: calculate covariance and correlation of Twitter sentiments and BTC exchange rate

```{r, tidy=TRUE}

btc_cov <- cov(btc_usd_tweets_combined$daily_avg_sent,btc_usd_tweets_combined$xchange_rate_change, method = "pearson")

btc_cov

```
A positive covariance means that the two variables tend to increase or decrease together. 
Correlation helps us analyze the effect of changes made in one variable over the other variable of the dataset.
Now that we know this, we should calculate the strength of the relationship between two, numerically measured, continuous variables.

```{r, tidy=TRUE}

btc_cor <- cor(btc_usd_tweets_combined$daily_avg_sent,btc_usd_tweets_combined$xchange_rate_change, method = "pearson")

btc_cor

```
> One of the most common ways to quantify a relationship between two variables is to use the Pearson correlation coefficient, which is a measure of the linear association between two variables.
>
> It always takes on a value between -1 and 1 where:
>
> * -1 indicates a perfectly negative linear correlation between two variables
> * 0 indicates no linear correlation between two variables
> * 1 indicates a perfectly positive linear correlation between two variables
>
> Often denoted as r, this number helps us understand the strength of the relationship between two variables. The closer r is to zero, the weaker the relationship between the two variables.

A weak correlation indicates that there is minimal relationship between the variables.

After reading some scientific papers I concluded that continuing down this path would bear no plausible outcome, so I decided to look at some other trend measures that seem promising.

***
## Fifth step: checking out Google Trends

Downloaded the data for Google search popularity of Bitcoin through Trendecon and Google Trends API.
Because of the limitations of standard Google Trends data I had to use the Trendecon package's <code>rts_gtrends_mwd</code> function to build a consistent daily time series.

> Construct a robust and consistent daily Time Series from Google Trends data. Daily, weekly and monthly Data is downloaded and consistently aggregated, using the Chow-Lin methodology.

```{r}

btc_ggl_trends <- read.csv("D:/Suli/Szakdolgozat1/data_to_be_cleaned/btc_google_trends.csv")

head(btc_ggl_trends)

```
Checking distribution:
```{r, tidy=TRUE, warning=FALSE, message=FALSE, fig.align='center'}

plot(density(btc_ggl_trends$value), type="n", main = "Distribution of Google Trends data")
polygon(density(btc_ggl_trends$value), col="red", border="gray")

```

***

## Sixth step: plotting Google Trends and BTC exchange rate change on scatterplot

```{r, tidy=TRUE, warning=FALSE, message=FALSE, fig.align='center'}
btc_usd_ggltrnds_combined <- read.csv("D:/Suli/Szakdolgozat1/clean data/Bitcoin_exchage_rates.csv")%>%
                             inner_join(btc_ggl_trends, by = c("Date" = "time")) %>%
                             mutate(xchange_rate_change = Close - Open) %>%
                             mutate(value = ifelse(xchange_rate_change < 0, value*-1, 
                                                              value)) %>%
                             select(-X) %>%
                             dplyr::rename(Trends_indicator = value)
```

```{r, tidy=TRUE, warning=FALSE, message=FALSE, fig.align='center'}
btc_ggltrnds_scatterplot <- plot_ly(data = btc_usd_ggltrnds_combined, y =  ~Trends_indicator, x = ~xchange_rate_change,
                            marker = list(size = 4,
                             color = 'rgba(255, 182, 193, .9)',
                             line = list(color = 'rgba(152, 0, 0, .8)', width = 1))) %>%
                            layout(yaxis = list(title = "Google Trends indicator"),
                                   xaxis = list(title = "BTC exchange rate change (USD)")) %>%
                            htmltools::div(align="center")

btc_ggltrnds_scatterplot

```

Plotting the absolute values shows the linearity between Google Trends indicator and BTC exchange rate change:

```{r, tidy=TRUE, warning=FALSE, message=FALSE, fig.align='center'}

ggl_trends_abs_scatterplt <- plot_ly(data = btc_usd_ggltrnds_combined ,y =  ~abs(Trends_indicator), x = 
                                       ~abs(xchange_rate_change),
                             marker = list(size = 4,
                             color = 'rgba(255, 182, 193, .9)',
                             line = list(color = 'rgba(152, 0, 0, .8)', width = 1))) %>%
                            layout(yaxis = list(title = "Google Trends indicator"),
                                   xaxis = list(title = "BTC exchange rate change (USD)")) %>%
                            htmltools::div(align="center" )
ggl_trends_abs_scatterplt

```
```{r, tidy=TRUE, warning=FALSE, message=FALSE, fig.align='center'}
ggscatter(btc_usd_ggltrnds_combined, x = "xchange_rate_change", y = "Trends_indicator", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "BTC exchange rate change (USD)", ylab = "Google Trends indicator")
```

> When you perform a statistical test a p-value helps you determine the significance of your results in relation to the null hypothesis.
> A p-value less than 0.05 (typically ≤ 0.05) is statistically significant. It indicates strong evidence against the null hypothesis, as there is less than a 5% probability the null is correct (and the results are random). Therefore, we reject the null hypothesis, and accept the alternative hypothesis.
> The alternative hypothesis states that the independent variable did affect the dependent variable, and the results are significant in terms of supporting the theory being investigated (i.e. not due to chance).
>
>`r tufte::quote_footer('https://www.simplypsychology.org/p-value.html')`

***
<!-- TODO: megnézni, hogy lehet tovább ezen finomítani, ugyanis nem abszolút értékes datasetnél gyenge/nem létező a kapcsolat -->

## Seventh step: calculate covariance and correlation of Google Trends and BTC exchange rate

Covariance:
```{r, tidy=TRUE}

print(cov(btc_usd_ggltrnds_combined$Trends_indicator,btc_usd_ggltrnds_combined$xchange_rate_change, method = "pearson"))

```
Correlation:
```{r, tidy=TRUE}

print(cor(btc_usd_ggltrnds_combined$Trends_indicator,btc_usd_ggltrnds_combined$xchange_rate_change, method = "pearson"))

```
There is a moderate uphill (positive) relationship.

## Eight step: incorporating more feature into the dataset

Chosen to improve model accuracy:

* US Dollar Bitcoin price/day
* Bitcoin transaction volume/day: The total estimated value in USD of transactions on the blockchain. This does not include coins returned as change.
* US Dollar transaction volume/day: The US Dollar value of bitcoins transacted on the blockchain.
* US Dollar exchange volume/day: The US Dollar trading volume of bitcoin on major bitcoin exchanges.
* Unique, used addresses/day

We need to combine all these to get a compact, usable dataframe.
First things first: Reddit submissions data cleaning.

>Lemmatisation (or lemmatization) in linguistics, is the process of grouping together the different inflected forms of a word so they can be analysed as a single item.

```{r, tidy = TRUE}
lemmatize_words_in_string <- function(col){
  for (i in 1:length(col)){
        col[i] <-  col[i] %>%
         strsplit(" ") %>%
         unlist() %>%
         lemmatize_words() %>%
         paste(collapse=" ")
  }
  return(col)
}
```

```{r, tidy=TRUE}
path <- "D:/Suli/Szakdolgozat1/data_to_be_cleaned/reddit_adat/bitcoin_sub"
bitcoin_sub_df <- list.files(path, pattern = "*.rds", full.names = TRUE) %>%
                  map_dfr(readRDS)

                
clean_bitcoin_sub_df <- bitcoin_sub_df %>%
                       filter(author != 'rBitcoinMod', author != 'crypto_bot', selftext != '[removed]' , 
                              selftext != '[deleted]') %>%
                       mutate(selftext = paste(title, selftext, sep = " ")) %>%
                       select(-title) %>%
                       mutate(selftext = tolower(selftext)) %>%
                       mutate(selftext = lemmatize_words_in_string(selftext)) %>%
                       mutate(selftext = gsub("[^\x01-\x7F]", "", selftext)) %>%
                       mutate(selftext = gsub("btc|xbt", "bitcoin", selftext)) %>%
                       mutate(selftext = gsub("cryptocurrency|cryptocurrencies", "crypto", selftext)) %>%
                       mutate(selftext = gsub("https?:\\/\\/\\S+","",selftext)) %>%
                       mutate(selftext = gsub("\\$|usd|dollars","dollar",selftext)) %>%
                       mutate(selftext = gsub("[[:punct:]]* *(\\w+[&'-]\\w+)|[[:punct:]]+ *| {2,}", " \\1",
                                              selftext)) %>%
                       mutate(created_utc = anydate(created_utc))
```

Looking at most frequent words used in the submissions:

```{r, tidy = TRUE}
stopwords <- data.frame(word = stopwords("eng"))

misc_df_word_freq <- clean_bitcoin_sub_df %>%
                  unnest_tokens(word,selftext) %>%
                  anti_join(stopwords)
```

```{r, tidy = TRUE}

frequent_words <- misc_df_word_freq %>%
                  select(word) %>%
                  dplyr::count(word) %>%
                  arrange(desc(n)) %>%
                  slice(-1,) %>%
                  top_n(20)

```

```{r, tidy = TRUE}
fig <-  plot_ly(
          data = frequent_words,
          x = ~word,
          y = ~n,
          type = "bar"
        ) %>% 
    layout(xaxis = list(categoryorder = "total descending"))
fig

```

Choose words which could be price indicative: buy, get, price, good, like, make, money, crypto, wallet and group the occurences of these by date. Interpolate missing values.

```{r, tidy = TRUE}
toMatch <- c("buy", "get", "price", "good", "like", "make", "money", "crypto", "wallet")
word_matches <- filter(misc_df_word_freq, word %in% toMatch) %>%
                select(created_utc, word) %>%
                group_by(created_utc, word) %>% 
                summarise(count = n()) %>% 
                ungroup() %>% 
                spread(word, count) %>%
                mutate(across(where(is.numeric), ~ ifelse(is.na(.), 0, .))) %>%
                pad() %>%
                mutate_at(toMatch, na.approx) %>%
                mutate_at(toMatch, round)
```

Plot of occurences over time:

```{r, tidy = TRUE}
fig <- plot_ly(data = word_matches, x = ~created_utc, y = ~buy, name = 'Buy', type= 'scatter', mode = 'lines', height = 500) %>%
  layout(title = "Number of occurences of possible price indicative words",
  paper_bgcolor='rgb(255, 255, 255)', plot_bgcolor='rgb(186, 186, 186)',
  xaxis = list(title = 'Date', range = list("2022-03-16 00:00:00", "2022-03-30 23:59:59"), rangeslider = list(type = "date", visible = T),
               list(dtickrange=list(NULL, 1000), value="%H:%M:%S.%L ms"),
               list(dtickrange=list(1000, 60000), value="%H:%M:%S s"),
               list(dtickrange=list(60000, 3600000), value="%H:%M m"),
               list(dtickrange=list(3600000, 86400000), value="%H:%M h"),
               list(dtickrange=list(86400000, 604800000), value="%e. %b d"),
               list(dtickrange=list(604800000, "M1"), value="%e. %b w"),
               list(dtickrange=list("M1", "M12"), value="%b '%y M"),
               list(dtickrange=list("M12", NULL), value="%Y Y"),
               rangeselector=list(
                 buttons=list(
                   list(count=1, label="1M", step="month", stepmode="backward"),
                   list(count=6, label="6M", step="month", stepmode="backward"),
                   list(count=1, label="1Y", step="year", stepmode="backward"),
                   list(count=1, label="YTD", step="year", stepmode="todate"),
                   list(step="ALL")
                 )),
               list(dtick = "M1", tickformat="%b\n%Y",
                    ticklabelmode="period")),
  yaxis = list(title = "Number of occurences",
               gridcolor = 'rgb(255,255,255)',
               showgrid = TRUE,
               showline = FALSE,
               showticklabels = TRUE,
               tickcolor = 'rgb(140, 140, 140)',
               ticks = 'outside',
               zeroline = FALSE)) %>%
         add_trace(y = ~crypto, name = 'Crypto', mode = 'lines') %>%
       add_trace(y = ~buy, name = 'Wallet', mode = 'lines') %>%
       add_trace(y = ~get,name = 'Get', mode = 'lines') %>%
       add_trace(y = ~good, name = 'Good', mode = 'lines') %>%
       add_trace(y = ~like, name = 'Like', mode = 'liness') %>%
       add_trace(y = ~make, name = 'Make', mode = 'lines') %>%
       add_trace(y = ~money, name = 'Money', mode = 'lines') %>%
       add_trace(y = ~price, name = 'Price', mode = 'lines') %>%
       add_trace(y = ~wallet, name = 'Wallet', mode = 'lines')

fig
rm(fig)
```

Correlation between the chosen words and Bitcoin exchange:

```{r, tidy = TRUE, echo=FALSE}
print("crypto-closing price:")
print(cor(word_matches$crypto,btc_usd_tweets_combined$Close))

print("make-closing price:")
print(cor(word_matches$make,btc_usd_tweets_combined$Close))

print("buy-closing price:")
print(cor(word_matches$buy,btc_usd_tweets_combined$Close))

print("get-closing price:")
print(cor(word_matches$get,btc_usd_tweets_combined$Close))

print("good-closing price:")
print(cor(word_matches$good,btc_usd_tweets_combined$Close))

print("like-closing price:")
print(cor(word_matches$like,btc_usd_tweets_combined$Close))

print("money-closing price:")
print(cor(word_matches$money,btc_usd_tweets_combined$Close))

print("make-closing price:")
print(cor(word_matches$make,btc_usd_tweets_combined$Close))

print("price-closing price:")
print(cor(word_matches$buy,btc_usd_tweets_combined$Close))

print("wallet-closing price:")
print(cor(word_matches$wallet,btc_usd_tweets_combined$Close))

```

Only moderate correlation has been found. Lastly, we should see if we find any correlation between Reddit sentiments and Bitcoin price change.

```{r, tidy = TRUE}
splitting_func <- function(string){
  strsplit(string, "(?<=[?.!\"\n])\\s?(?=[a-z])", perl=T)
}
```

```{r, tidy = TRUE}

sent_bitcoin_sub_df <- bitcoin_sub_df %>%
                       filter(author != 'rBitcoinMod', author != 'crypto_bot', selftext != '[removed]' , 
                              selftext != '[deleted]') %>%
                       mutate(selftext = paste(title, selftext, sep = ".")) %>%
                       select(c(-num_comments,-title,-score,-subreddit,-id,-author)) %>%
                       mutate(selftext = tolower(selftext)) %>%
                       mutate(selftext = lemmatize_words_in_string(selftext)) %>%
                       mutate(selftext = gsub("[^\x01-\x7F]", "", selftext)) %>%
                       mutate(selftext = gsub("btc|xbt", "bitcoin", selftext)) %>%
                       mutate(selftext = gsub("cryptocurrency|cryptocurrencies", "crypto", selftext)) %>%
                       mutate(selftext = gsub("https?:\\/\\/\\S+","",selftext)) %>%
                       mutate(selftext = gsub("\\$|usd|dollars","dollar",selftext)) %>%
                       mutate(created_utc = anydate(created_utc)) %>%
                       unnest_tokens(tbl = ., input = selftext, output = sentences, token = splitting_func) %>%
                       mutate(sentences = gsub("[[:punct:]]* *(\\w+[&'-]\\w+)|[[:punct:]]+ *| {2,}", " \\1",
                                              sentences))
```

```{r, tidy = TRUE}
reddit_vader_df <- NULL

for (i in 1:nrow(sent_bitcoin_sub_df)){
  outs <-  vader_df(sent_bitcoin_sub_df$sentences[i])
  reddit_vader_df <- rbind(reddit_vader_df,outs)
}

```

```{r, tidy = TRUE, eval = FALSE}
write_rds(reddit_vader_df,"D:/Suli/Szakdolgozat1/data_to_be_cleaned/reddit_adat/bitcoin_sub/reddit_vader_df.rds")
```

```{r, tidy = TRUE}

reddit_vader_df <- readRDS("D:/Suli/Szakdolgozat1/data_to_be_cleaned/reddit_adat/reddit_vader_df.rds") %>%
                   cbind(sent_bitcoin_sub_df) %>%
                   select(c(compound,pos,neu,neg,-sentences,created_utc)) %>%
                   mutate(across(c(pos,neg,neu),~replace_na(.,0))) %>%
                   mutate(positive = case_when(pos >= 0.2 ~ 1, pos < 0.2 ~ 0),
                          negative = case_when(neg >= 0.2 ~ 1, neg < 0.2 ~ 0)) %>%
                   select(created_utc,positive,negative) %>%
                   group_by(created_utc) %>%
                   summarise(total_positive = sum(positive), total_negative = sum(negative)) %>%
                   pad() %>%
                   mutate(across(c(total_positive,total_negative), na.approx)) %>%
                   mutate(across(c(total_positive,total_negative), round))

```

```{r, tidy = TRUE}
btc_usd_ggltrnds_combined <- btc_usd_ggltrnds_combined %>% 
                             filter(row_number() <= n()-1) %>%
                             cbind(reddit_vader_df) %>%
                             select(-created_utc)
```

```{r, tidy=TRUE, warning=FALSE, message=FALSE, fig.align='center'}
plot(density(btc_usd_ggltrnds_combined$total_positive), type="n", main = "Distribution of total positives")
polygon(density(btc_usd_ggltrnds_combined$total_positive), col="red", border="gray")
```

```{r, tidy = TRUE}

fig <- plot_ly(btc_usd_ggltrnds_combined, x = ~Date, y = ~total_negative, type = 'bar', name = 'Negatives/day') %>%
  add_trace(y = ~total_positive, name = 'Positives/day') %>% 
  layout(yaxis = list(title = 'Count'), barmode = 'group') %>%
  add_trace(y = ~Close*(1/1000), type = 'scatter', mode = 'lines', name = 'Bitcoin closing price')

fig
```

Correlation between Bitcoin price change and total positives/negatives:

```{r, tidy = TRUE}

print(cor(btc_usd_ggltrnds_combined$Close,btc_usd_ggltrnds_combined$total_positive))

print(cor(btc_usd_ggltrnds_combined$Close,btc_usd_ggltrnds_combined$total_negative))

```
```{r, tidy = TRUE}

misc_df <- sent_bitcoin_sub_df %>%
            mutate(n = 1) %>%
            select(-sentences) %>%
            group_by(created_utc) %>%
            summarise(number_of_posts = sum(n)) %>%
            pad() %>%
            mutate(number_of_posts= round(na.approx(number_of_posts))) %>%
            cbind(btc_usd_ggltrnds_combined) %>%
            select(-Date)
                    
```

```{r, tidy=TRUE, warning=FALSE, message=FALSE, fig.align='center'}
plot(density(misc_df$number_of_posts), type="n", main = "Distribution of total positives")
polygon(density(misc_df$number_of_posts), col="red", border="gray")
```

```{r,tidy = TRUE}
print(cor(misc_df$Close,misc_df$number_of_posts))
```
Well, this shows a moderate amount of correlation between the number of Reddit posts and Bitcoin closing price.
Now with Tweet amount:

```{r, tidy = TRUE}

tweets <- read_csv("D:/Suli/Szakdolgozat1/data_to_be_cleaned/twitter_adat/n_of_tweets_#bitcoin.csv")

```

```{r, tidy = TRUE}

formatted_tweets <- tweets %>%
                    rename(date = V1) %>%
                    rename(number_of_tweets = V2)

```

```{r, tidy = TRUE}

df_with_nr_of_tweets <- misc_df %>%
            inner_join(formatted_tweets, by = c("created_utc" = "date")) %>%
            select(c(-total_positive,-total_negative)) %>%
            mutate(number_of_tweets= round(na.approx(number_of_tweets)))

```

```{r, tidy = TRUE}

print(cor(df_with_nr_of_tweets$Close, df_with_nr_of_tweets$number_of_tweets, method = "pearson"))

```
Incorporating all features into the dataset, then making a correlation matrix to check for multicollinearity:

```{r, tidy = TRUE}

temp <-do.call(cbind,
            lapply(list.files(path = "D:/Suli/Szakdolgozat1/data_to_be_cleaned/", pattern = "*.xlsx", full.names = TRUE)
                 , readxl::read_xlsx)) %>%
       select(c(Nr_of_Bitcoin_transactions, Nr_of_unique_Bitcoin_addresses, Bitcoin_transaction_volume
                , Wikipedia_searches_Bitcoin))

```

```{r, tidy = TRUE}

final_df <- df_with_nr_of_tweets %>%
            cbind(temp) %>%
            select(c(-Open,-Low,-High,-Adj.Close,-Volume)) %>%
            dplyr::rename(Price_change = xchange_rate_change, Date = created_utc, Nr_of_tweets = number_of_tweets,
                          Nr_of_Reddit_posts = number_of_posts, Closing_price = Close,
                          Google_Trends_indicator = Trends_indicator)
            
```


```{r, tidy = TRUE}

cor(final_df[,2:10])

```
The correlation matrix doesn't show anything outstanding, we can assess feature importance in the ML notebook.

Exporting final dataframe:

```{r, tidy = TRUE, eval = FALSE}

write_xlsx(final_df, "D:/Suli/Szakdolgozat1/clean data/data_for_training.xlsx")

```


With all of these in order we can start tweaking the Prophet model.
